A Computational Account of Default-Mode Function\\by Control Theory and Reinforcement Learning

### 2016-07-15 paper.tex
hipp comments
new anat notes

\item
RTPJ:

@@

\item
the GMV of the entorhinal cortex (connectionally and functionally closely coupled with the HC) correlated with social network size (Kanai et al., 2012)
\end{itemize}
\end{itemize}

>>>>

RTPJ:
\item
Corbetta2008:
Although both attentional networks have been most exten- sively investigated in vision, the available evidence indicates a supramodal function (Driver and Spence, 1998; Macaluso et al., 2002). The ventral network (right TPJ, right IFG) registers salient events in the environment not only in the visual but also in the auditory and tactile modalities (Downar et al., 2000)
Several lines of evidence indicate that two cortico-cortical neural systems are involved in attending to environmental stimuli (Corbetta and Shulman, 2002). A dorsal frontoparietal network. A second system, the ventral frontoparietal network, is not ac- tivated by expectations or task preparation but responds along with the dorsal network when behaviorally relevant objects (or targets) are detected (Corbetta et al., 2000). Both dorsal and ventral networks are also activated during reorienting, with en- hanced responses during the detection of targets that appear at unattended locations. For example, enhanced responses are observed when subjects are cued to expect a target at one location but it unexpectedly appears at another (i.e., ‘‘invalid’’ targets in the Posner spatial cueing paradigm)
or when a target appears infre- quently, as in ‘‘oddball’’ paradigms.

Intimately related to prediction error signaling:
An early theory of how the two networks interact (Corbetta and Shulman, 2002) proposed that when attention is reoriented to a new source 
of information (stimulus-driven reorienting), output from the ven- tral network interrupts (as a ‘‘circuit breaker’’) ongoing selection in the dorsal network, which in turn shifts attention toward the novel object of interest.

relevance is the critical factor that determines whether an object activates the ventral network (Downar et al., 2001). The ventral network might be considered a prime candi-date for mediating orienting to salient but unimportant stimuli, i.e., exogenous attention (Posner and Cohen, 1984), be- cause under passive conditions it is highly responsive to distinctive sensory
events in all modalities (Downar et al., 2000). The ventral network is well activated by stimuli that are important, even if they are not very distinctive. 
CURRENT OPINION: VA network does underlie  stimulus-driven reorienting to environmental stimuli based on their task relevance. An important conclusion from these neuroimaging studies is that the psychological dis- tinction between exogenous and endogenous orienting (Jo- nides, 1981) may not map onto different neural systems.

@@

\item
the GMV of the entorhinal cortex (connectionally and functionally closely coupled with the HC) correlated with social network size (Kanai et al., 2012)

\item 
In fact, phase-locked hippocampal?<80><93>cortical loops have been proposed t
formation of mnemonic neuronal representations
**a large body of animal and human literature relates
hippocampal-prefrontal theta to memory and memory to the DMN**

\item 
A special case is the hippocampus whose highly recursive connection matrix is thought to function as a large ‘autoassocia- tor’, allowing the reconstruction of entire episodes from remembered fragments.

\item
hippocampal pyramidal cells during rest and sleep produce strongly coherent ensemble bursts believed to be critical in transferring information to the neocortex.

\item
sequential single- cell recording could reveal such cooperative patterns

\item
buszaki2004 theta oscillations:
Using large-scale recordings, researchers can follow complex patterns for extended time periods and determine whether their modification by experience will influence self-generated patterns in the absence of envi- ronmental inputs. Spike sequences, imposed upon the network by behavioral manipulations, recur spontaneously during subsequent sleep
indicating that neurons organize themselves into preferred cell assemblies, and the seeds of emergence stem from experi- ence-related activity.
 Such internally driven, self-organized assemblies may reflect mechanisms that give rise to cognitive phenomena
 Sharp-wave ripples are believed to be the transfer mechanism of information from the hippocampus to neocortex during off-line (eg, sleep) states.
Neurons, mostly studied in the hippocampus, which fire action potentials only when the animal is in a specific place in a given environment (that place where a cell fires is called the “place field” of that cell).
-> self-play in deepmind Go

\item
statistical structure of hippocampal activity ->
spatial maps of surroundings are encoded

\item
Numerous experiments have demonstrated that hippocampal neurons show place-related firing while the rat explores or traverses its environment so that each assembly of hippocampal principal cells defines a particular position of space

\item
Diba + Buzsaki 2007
We report that temporal spike sequences from hippocampal place neurons of rats on an elevated track recurred in reverse order at the end of a run, but in forward order in anticipation of the run, coinciding with sharp waves. Vector distances between the place fields were reflected in the temporal structure of these sequences. This bidirectional re-enactment of temporal sequences may contribute to the establishment of higher-order associations in episodic memory.

\item
coding, transfer, and consolidation of
information
This emerging picture of hippocampal dy- namics suggests that neurons at the opposite ends of the distributions may convey differ- ent but complementary types of information. The ever-active minority of place cells may be responsible for generalizing across envi- ronments and affords the brain the capacity to regard no situation as completely un- known because every alley, mountain, river, or room has elements of previously experi- enced similar situations. In many situations,
this minority provides the “best guess” of the hippocampus and offers “good enough” solutions to get by. On the other hand, the majority of less active neurons constitute a large reservoir that can be mobilized (7) to precisely distinguish one situation from an- other and incorporate novel ones as distinct.
